Historian: accurate reconstruction of ancestral sequences and evolutionary rates

### 2016-12-11 doc/paper.tex
refactored docs

\abstract{
{\bf Motivation.}
Reconstruction of ancestral sequence histories,
and estimation of parameters like indel rates,
are improved by using explicit evolutionary models
and summing over uncertain alignments.
%The best alignment tools for ancestral reconstruction
%are not necessarily those that agree most closely with benchmark datasets based on 3D structure alignments.
The previous best tool for this purpose (according to simulation benchmarks)
was ProtPal, but this tool was too slow for practical use.
{\bf Results.}
Historian combines an efficient reimplementation of the ProtPal algorithm with performance-improving heuristics from other alignment tools.
Simulation results on fidelity of rate estimation via ancestral reconstruction,
along with evaluations on the structurally-informed alignment dataset BAliBase 3.0,
recommend Historian over other alignment tools for evolutionary applications.
{\bf Availability and Implementation.}
Historian is available at \url{https://github.com/ihh/indelhistorian} under the Creative Commons Attribution 3.0 US license.
{\bf Contact.}
Ian Holmes {\tt ihholmes+historian@gmail.com}.
{\bf Supplementary Information.}
None.
}

>>>>

\structabs{
Reconstruction of ancestral sequence histories,
and estimation of parameters like indel rates,
are improved by using explicit evolutionary models
and summing over uncertain alignments.
%The best alignment tools for ancestral reconstruction
%are not necessarily those that agree most closely with benchmark datasets based on 3D structure alignments.
The previous best tool for this purpose (according to simulation benchmarks)
was ProtPal, but this tool was too slow for practical use.
}{
Historian combines an efficient reimplementation of the ProtPal algorithm with performance-improving heuristics from other alignment tools.
Simulation results on fidelity of rate estimation via ancestral reconstruction,
along with evaluations on the structurally-informed alignment dataset BAliBase 3.0,
recommend Historian over other alignment tools for evolutionary applications.
}{
Historian is available at \url{https://github.com/ihh/indelhistorian} under the Creative Commons Attribution 3.0 US license.
}{
Ian Holmes {\tt ihholmes+historian@gmail.com}.
}{
None.
}
